Evaluation of the repository

### 2024-11-28 pages/paper_evaluation.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid

@@

```{python}
import pandas as pd
import plotly.express as px
from functions import eval_chart, plot_scatter, calculate_scores

# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 5, 4, 1],
  'Lim et al. 2020': [15, 3, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [16, 1, 2, 5],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

eval_chart(stress_wide)
```

@@

eval_chart(ispor_wide)
```

@@

eval_chart(criteria_wide)
```

@@

eval_chart(criteria_wide)
```

>>>>

```{python}
# Imports and functions
import pandas as pd
import plotly.express as px
import plotly.express as px
import plotly.io as pio
from functions import eval_chart, plot_scatter, calculate_scores
```

@@

```{python}
# Create dataframe of results
col = ['fully', 'partially', 'not', 'na']
stress_dict = {
  'Shoaib and<br>Ramamohan 2021': [17, 6, 1, 0],
  'Huang et al. 2019': [14, 5, 4, 1],
  'Lim et al. 2020': [15, 3, 3, 3],
  'Kim et al. 2021': [15, 5, 2, 2],
  'Anagnostou et al. 2022': [14, 2, 5, 3],
  'Johnson et al. 2021': [16, 1, 2, 5],
  'Hernandez et al. 2015': [18, 2, 3, 1],
  'Wood et al. 2021': [22, 2, 0, 0]
}
stress_wide = pd.DataFrame(stress_dict, index=col).T

eval_chart(stress_wide).show(config={'displayModeBar': False})
```

@@

eval_chart(ispor_wide).show(config={'displayModeBar': False})
```

@@

# Create figure
stress_chart = eval_chart(criteria_wide)

# Display figure
stress_chart.show(config={'displayModeBar': False})

# Save figure as 300DPI static image for use in article
pio.write_image(stress_chart, '../images/stress_criteria.png',
                width=2.8*300, height=2.5*300, scale=1)
```

@@

# Create figure
ispor_chart = eval_chart(criteria_wide)

# Display figure
ispor_chart.show(config={'displayModeBar': False})

# Save figure as 300DPI static image for use in article
pio.write_image(ispor_chart, '../images/ispor_criteria.png',
                width=2.5*300, height=2*300, scale=1)

```

### 2024-11-28 pages/repo_evaluation.qmd
feat(images): making eval_charts (a) save to png, (b) colourblind friendly, (c) percentage overlaid

```{python}
# Imports and function
import plotly.express as px
import pandas as pd
from functions import eval_chart, plot_scatter
```

@@

eval_chart(criteria_wide)
```

@@

eval_chart(badge_wide)
```

@@

eval_chart(essential_wide)
```

@@

eval_chart(optional_wide)
```

@@

eval_chart(badges_wide)
```

@@

# Create figure
eval_chart(badges_fig)
```

@@

eval_chart(stars_wide)
```

>>>>

```{python}
# Imports and function
import plotly.express as px
import plotly.io as pio
import pandas as pd
from functions import eval_chart, plot_scatter
```

@@

eval_chart(criteria_wide).show(config={'displayModeBar': False})
```

@@

eval_chart(badge_wide).show(config={'displayModeBar': False})
```

@@

eval_chart(essential_wide).show(config={'displayModeBar': False})
```

@@

eval_chart(optional_wide).show(config={'displayModeBar': False})
```

@@

eval_chart(badges_wide).show(config={'displayModeBar': False})
```

@@

# Create figure
eval_chart(badges_fig).show(config={'displayModeBar': False})
```

@@

# Create figure
stars_chart = eval_chart(stars_wide)

# Display figure
stars_chart.show(config={'displayModeBar': False})

# Save figure as 300DPI static image for use in article
pio.write_image(stars_chart, '../images/stars_criteria.png',
                width=2.5*300, height=1.8*300, scale=1)
```
